Novel lattice Boltzmann method for simulation of strongly shear thinning viscoelastic fluids

### 2023-11-27 NovelLBM.tex
Nozzle

	\subsection{Comparison with literature}
	Malaspinas et al.\cite{ma2020} provide a detailed validation and claim very high accuracy. Therefore, we pick this as a comparison. We aim at the reproduction of figures 17 and 18 from said paper. We calculate this 2D flow in 3D as the viscoelastic algorithm has not been validated for 2D velocity sets. Otherwise the geometry is identical. It is not entirely clear to us, how they define typical scales. We define the typical velocity as the maximum velocity, as is likely done in the paper. The typical length, we set as half of the channel width. We define the typical shear rate as typical velocity divided by typical length. We set $\eta_\text{s} = \SI{1}{\milli\pascal\second}$ as the paper only gives ratios, and it probably does not matter here. Nevertheless, our lattice units do not line up exactly with those from Malaspinas, as our viscosity is different due to the shuffling.
	%Beware equation 61 in the paper is wrong. It should have an 8 instead of the 4.
	The parameters from the paper ($R_\nu$, $Wi$ and $N$) are varied as in the paper. The error is calculated as follows.
	\begin{equation}\label{eq:l2error}
		E_\text{u} = \frac{1}{u_\text{max}}\sqrt{\frac{1}{N}\sum\abs{u_\text{simulation}-u_\text{theory}}^2}
	\end{equation}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/malaspinas2010.eps}
		\caption{Double logarithmic plot of the L2 error as defined in equation \ref{eq:l2error} from Malaspinas et al.\cite{malaspinas2010} (dots) compared to our algorithm (x) as a function of grid resolution.}
		\label{fig:malaspinas2010}
	\end{figure}
	As can be seen in figure \ref{fig:malaspinas2010}, our results notably do not depend on the Weissenberg Number. While our error decreases with N with a constant power, Malaspinas et al. see diminishing returns. While these results are excellent, the error in our implementation is still dependent on the viscosity ratio. When going to significantly higher ratios, this needs to be checked to ensure it does not get too large.\todo{link to appendix where we validate this}
	With this, one can see, that we are not only capable to simulate parameters not yet accessible, but our implementation is also better for the parameters used in literature. Knowing our simulations to be good we in the following show results for interesting systems, that are not analytically solvable.
	\section{Results for non analytically solvable systems}\todo{do all of these with MC}
	\subsection{Conical nozzle}
	\todo{do}
	\subsection{Cell in shear flow}
	\todo{do}
	\subsection{RT-DC}
	\todo{do}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/RT-DC_v.eps}
		\caption{Plot of the velocity in the RT-DC channel.}
		\label{fig:RT-DC_v}
	\end{figure}
	\begin{figure}[H]
	\centering
	\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/RT-DC_tau.eps}
	\caption{Plot of the polymer stress in the RT-DC channel.}
	\label{fig:RT-DC_tau}
	\end{figure}

@@

>>>>

	\subsection{Comparison with literature}
	Malaspinas et al.\cite{ma2020} provide a detailed validation and claim very high accuracy. Therefore, we pick this as a comparison. We aim at the reproduction of figures 17 and 18 from said paper. We calculate this 2D flow in 3D as the viscoelastic algorithm has not been validated for 2D velocity sets. Otherwise the geometry is identical. It is not entirely clear to us, how they define typical scales. We define the typical velocity as the maximum velocity, as is likely done in the paper. The typical length, we set as half of the channel width. We define the typical shear rate as typical velocity divided by typical length. We set $\eta_\text{s} = \SI{1}{\milli\pascal\second}$ as the paper only gives ratios, and it probably does not matter here. Nevertheless, our lattice units do not line up exactly with those from Malaspinas, as our viscosity is different due to the shuffling.
	%Beware equation 61 in the paper is wrong. It should have an 8 instead of the 4.
	The parameters from the paper ($R_\nu$, $Wi$ and $N$) are varied as in the paper. The error is calculated as follows.
	\begin{equation}\label{eq:l2error}
		E_\text{u} = \frac{1}{u_\text{max}}\sqrt{\frac{1}{N}\sum\abs{u_\text{simulation}-u_\text{theory}}^2}
	\end{equation}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/malaspinas2010.eps}
		\caption{Double logarithmic plot of the L2 error as defined in equation \ref{eq:l2error} from Malaspinas et al.\cite{malaspinas2010} (dots) compared to our algorithm (x) as a function of grid resolution.}
		\label{fig:malaspinas2010}
	\end{figure}
	As can be seen in figure \ref{fig:malaspinas2010}, our results notably do not depend on the Weissenberg Number. While our error decreases with N with a constant power, Malaspinas et al. see diminishing returns. While these results are excellent, the error in our implementation is still dependent on the viscosity ratio. When going to significantly higher ratios, this needs to be checked to ensure it does not get too large.\todo{link to appendix where we validate this}
	With this, one can see, that we are not only capable to simulate parameters not yet accessible, but our implementation is also better for the parameters used in literature. Knowing our simulations to be good we in the following show results for interesting systems, that are not analytically solvable.
	\section{Results for non analytically solvable systems}\todo{do all of these with MC}\todo{Do we want walls?}
	\subsection{Conical nozzle}
	\todo{do}
		\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/Nozzle_v.eps}
		\caption{Plot of the velocity in a conical nozzle.}
		\label{fig:Nozzle_v}
	\end{figure}
	\subsection{Cell in shear flow}
	\todo{do}
	\subsection{RT-DC}
	\todo{do}
	\begin{figure}[H]
		\centering
		\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/RT-DC_v.eps}
		\caption{Plot of the velocity in the RT-DC channel.}
		\label{fig:RT-DC_v}
	\end{figure}
	\begin{figure}[H]
	\centering
	\adjincludegraphics[trim=0 0 0 0, clip, scale=1]{assets/plots/RT-DC_tau.eps}
	\caption{Plot of the polymer stress in the RT-DC channel.}
	\label{fig:RT-DC_tau}
	\end{figure}

@@

	\subsection{Viscoelastic Reynolds-Scaling}
	Does not reproduce transitory behavior\todo{NEEDS TO WORK}
